Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-11-30 src/tex/ms.tex
Added plot with marginalized u

\note{Think about what I want to do here.}
For example, we randomly select \note{N} galaxies and estimate redshift posteriors while marginalizing over the $u$ band.
These posteriors can be seen in Figure \note{N}.
Mention how the loss of information degrades the posteriors.

>>>>

\begin{figure}[t!]
    \script{photo-z/plot_marginalized_posterior.py}
    \begin{centering}
        \includegraphics{figures/posterior_marginalized.pdf}
        \caption{
            Redshift posteriors for an example galaxy.
            The vertical red line indicates the true redshift.
            The black posterior is estimated using the information from all 6 LSST bands (and includes convolution of the photometric errors).
            The gold posterior has had the $u$ band marginalized, which opens up a second high-redshift mode.
        }
        \label{fig:posterior_marginalized}
    \end{centering}
\end{figure}

Figure \ref{fig:posterior_marginalized} compares posteriors with and without $u$ band information for an example galaxy.
It is clear how losing the $u$ band information increases the uncertainty in the redshift inference.
In this instance, a second potential redshift mode is created.
Conversely, this demonstrates how the addition of $u$ band information rules out the higher redshift solution for this galaxy.
